---
title: "Inflation Data"
author: "Aaron Peikert"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  tufte::tufte_html: default
  tufte::tufte_handout: default
repro:
  packages:
  - here
  - tidyverse
  - lubridate
  - aaronpeikert/repro@fc7e884
  scripts: R/prepare_inflation.R
  data: data/raw/inflation.rds
---

```{r setup, include=FALSE}
repro::automate_load_packages()
repro::automate_load_scripts()
knitr::opts_chunk$set(echo = FALSE)
```

## This is a test 
# This is another test

This is **bold**, while this is *italic*.

The dataset we use stems from the [Bank of England Research datasets](https://www.bankofengland.co.uk/statistics/research-datasets).

I quote:

> This dataset contains the individual responses to our Inflation Attitudes Survey, a quarterly survey of people’s feelings about inflation and other economic variables like the interest rate. 

```{r load-inflation}
# code chunks can come from other scripts, this one is loaded from:
# `R/prepare_inflation.R`
```

```{r transform-inflation}
# this chunk is also loaded from the same script
# note that they must be empty and the names must correspond
```

For this dataset the Bank of England asked `r prettyNum(nrow(inflation), big.mark = ".", decimal.mark = ",")` people for their opinion on the perceived and expected inflation.
The survey has run quarterly since `r min(inflation$year)`.

```{r}
inflation %>% 
  group_by(date) %>% 
  summarise(across(c(perception, expectation),
                   ~ mean(., na.rm = TRUE)),
            .groups = "drop") %>% 
  pivot_longer(c(expectation, perception)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_line(aes(date, value, color = name)) +
    theme_minimal() +
  ylab("subjective inflation in %-points") +
  labs(color = "") +
  theme(legend.position = c(.15, .9)) +
  NULL 
  
```


```{r}

with(mtcars, plot(hp, mpg))

```

This is an inline R test: `r 9+3` Great. 

```{python}

print("Hello World! Python here, do you miss R already?")

```

```{r}

# use a function without loading the package:
# package::function
usethis::use_git_config(
  user.name = "Jens Fuenderich", # <-- change to your name
  user.email = "Jens.Fuenderich@uni-erfurt.de", # <-- and your email
  init.defaultBranch = "main") # <-- not necessary but kinder than 'master'

```




